From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-07-22 dictionary.tex
Minor change in the Notations section.

It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an \'etale group scheme; this does not imply that $\pi_0(G)$ is finite.
If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group; in this case, $\pi_0(G)$ is finite. 
Indeed, a smooth commutative group scheme $G$ is an algebraic group if and only if the \'etale group scheme $\pi_0(G)$ is finite.

@@

\subsection{Examples}

>>>>

It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type, being smooth.
If the structure morphism $G \to \Spec{\Fq}$ is also \'etale, then $G$ is an \'etale group scheme; this does not imply that $\pi_0(G)$ is finite.
An algebraic group over $\Fq$ is a smooth group scheme of finite type, in which case its component group scheme is finite.

@@
